Constraint result to the self-interacting dark matter model without dark energy in cosmology

### 2025-03-17 article/article.tex
add introduction in the article

   \title{Self-interacting dark matter model without dark energy in cosmology}

@@

@@

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
   \cite{Borghi_2022};\cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
   the BAO data from SDSS and DESI 2024.

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}[-4(\kappa C_1)^2+9H_0^2\Omega_{1,0}]}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+\frac{t_0}{2H_0\Omega_{1,0}}\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}[htbp]
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
   \end{figure}

>>>>

   \title{Constraint result to the self-interacting dark matter model without dark energy
   in cosmology}

@@

   The standard Λ-Cold Dark Matter (ΛCDM) model has been remarkably 
   successful in explaining a wide range of cosmological observations, 
   from the Cosmic Microwave Background (CMB) anisotropies to 
   large-scale structure formation. However, there are also many 
   alternative models that have been proposed to explain the
   accelerated expansion of the Universe, such as the dynamical
   dark energy models and the modified gravity models.

   It has been shown that dark matter self-interaction could distribute 
   to the accelerated expansion without dark energy component. According
   to the Boltzmann formalism, the disequilibrium between dark matter particle
   creation and annihilation processes would creat an effective source term 
   making negative pressure just like the dark energy. \cite{refId0}
   investigated the analytical solutions for the simple interacting dark matter (IDM) 
   model, and find that the effective annihilation term is much smaller than the
   results given by the general methods. The gravitational matter creation
   model is mathematically equivalent to one case of the IDM models.

   In this paper, we use the newly revised data from $H(z)$, supernovae Ia, 
   quasars and baryon acoustic oscillation by using the Markov chain Monte
   Carlo (MCMC) method. The result gives that the lower limit of the interacting
   dark matter particle mass is about 1 eV.

@@

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
   \cite{Borghi_2022};\cite{Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
   the BAO data from SDSS and DESI 2024.

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}[-4(\kappa C_1)^2+9H_0^2\Omega_{1,0}]}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}[htbp]
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
   \end{figure}
